Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review

### 2021-03-29 Article.Rmd
Literature search
Updating scripts and Article.Rmd for better readability

@@

```{r General_characteristics_data_preparation, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
source("./scripts/read_overview.R", local = knitr::knit_global())
source("./scripts/create_year_data.R", local = knitr::knit_global())
source("./scripts/create_design_data.R", local = knitr::knit_global())
source("./scripts/create_location_data.R", local = knitr::knit_global())

>>>>

knitr::knit_exit()

@@

```{r General_characteristics_data_preparation, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
#Load required packages :
library(tidyverse)
library(readr)

#Load the data from the .csv files
source("./scripts/read_overview.R", local = knitr::knit_global())

#Source the scripts used to manipulate the data from the .csv files
source("./scripts/create_year_data.R", local = knitr::knit_global())
source("./scripts/create_design_data.R", local = knitr::knit_global())
source("./scripts/create_location_data.R", local = knitr::knit_global())
